---
title: "Swiss TPH Word report example"
subtitle: "Sub-Title of Document Name of Project/Mandate, etc…"
author:
  - name: Jane Doe
    affiliations:
      - ref: stph
      - ref: unibas
    corresponding: true
    email: jand.doe@swisstph.ch
    equal-contributor: true
    orcid: 0000-0000-0000-0000
  - name: John Doe
    affiliations:
      - ref: unibas
    equal-contributor: true
    orcid: 0000-0000-0000-0000
affiliations:
  - id: stph
    name: Swiss Tropical and Public Health Institute, Basel, Switzerland
  - id: unibas
    name: University of Basel, Basel, Switzerland
date: today
editor: source
execute:
  echo: false
  warning: false
filters:
  - word-report                                              # MANDATORY: Swiss TPH filter (do not remove/rename)
format:
  docx:
    number-sections: true
    reference-doc: _extensions/word-report/report_template2.docx  # MANDATORY: Swiss TPH template (keep path inside _extensions/)
---

```{=html}
<!--
================================================================================
GUIDE TO THE YAML HEADER ABOVE  (this block is a comment; it does NOT render)
================================================================================

HOW TO RENDER (two equivalent ways):

  Manual : put this .qmd and the _extensions/word-report/ folder in the same
           directory, then run `quarto render word_report_demo.qmd` (or click
           Render in RStudio).
  Helper : stphtoolbox::generate_word_report("word_report_demo.qmd", "my_report")
           does exactly the same — it copies _extensions/word-report/ next to
           the .qmd for you and renders. The helper REQUIRES the two MANDATORY
           lines below; it refuses to render a .qmd without them.

SAFE TO CUSTOMISE — change these freely:

  title / subtitle:
            Document title and subtitle. Any text.

  author:   List of authors. Edit the values (name, email, orcid,
            corresponding, equal-contributor) freely, and add/remove whole
            author entries. KEEP the structure (each entry is a "- name:" with
            its indented fields).
            GOTCHA: each author's "- ref:" under affiliations MUST match an
            "id:" in the affiliations block below. ref: stph -> id: stph.
            A ref with no matching id drops the affiliation silently.

  affiliations:
            Defines the organisations referenced above. Edit id/name, add or
            remove entries. If you rename an "id:", update every author "ref:"
            that points to it.

  date:     "today" auto-fills the render date. Can also be a fixed date
            (e.g. 2026-06-15) or removed.

  editor:   RStudio editing mode only (visual vs source). No effect on the
            rendered .docx. Safe to change or remove.

  number-sections: true
            Toggles automatic heading numbers. true/false — safe to flip.

CHANGE ONLY IF YOU KNOW WHAT YOU ARE DOING — these can break rendering:

  execute: { echo: false, warning: false }
            Hides R code and warnings. Setting echo: true dumps R source into
            the document body.

  filters:
    - word-report
            Activates the Swiss TPH "word-report" Quarto extension (lives in
            _extensions/word-report/). Removing this line drops the Swiss TPH
            formatting. Do NOT delete or rename.

  format: docx -> reference-doc: _extensions/word-report/report_template2.docx
            The Word template supplying Swiss TPH styles (headings, cover,
            fonts). The path points INTO the _extensions/ folder — do NOT move,
            rename, or relocate _extensions/ or this .docx, or the render fails
            or loses all styling.
================================================================================
-->
```

```{r}
# Reader
library(readr)

# Data processing
library(dplyr)

# Data visualisation
library(scales)
library(ggplot2)

library("stphtoolbox")
```

# Executive summary {.unnumbered}

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators. To achieve this, it would be necessary to have uniform grammar, pronunciation and more common words. If several languages coalesce, the grammar of the resulting language is more simple and regular than that of the individual languages. The new common language will be more simple and regular than the existing European languages. It will be as simple as Occidental; in fact, it will be Occidental. To an English person, it will seem like simplified English, as a sceptical Cambridge friend of mine told me what Occidental is. The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary.

The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators.

# Example Heading 1

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words.

## Example Heading 2

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators. To achieve this, it would be necessary to have uniform grammar, pronunciation and more common words. If several languages coalesce, the grammar of the resulting language is simpler and more regular than that of the individual languages.

### Example Heading 3

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators. To achieve this, it would be necessary to have uniform grammar, pronunciation and more common words. If several languages coalesce, the grammar of the resulting language is simpler and more regular than that of the individual languages.

#### Example Heading 4

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation.

# Graphical chart colors

```{r}
# Load Swiss TPH graphical chart colors
stph_colors <- stphtoolbox::stph_palette()
scales::show_col(stph_colors)
```

# Table design

```{r}
library(dplyr)
iris %>%
  head(10) %>% 
  knitr::kable()
```

```{r}
iris %>% 
  stphtoolbox::vertical_boxplot("Sepal.Length",
                                "Species")
```