---
title: "Swiss TPH report example"
subtitle: "Sub-Title of Document Name of Project/Mandate, etc…"
author:
  - name: Jane Doe
    orcid: 0000-0000-0000-0000
  - name: John Doe
    orcid: 0000-0000-0000-0000
date: today
editor: visual
execute:
  echo: false
  warning: false
format: docx
metadata-files:
  - _word_metadata.yml
---

```{r}
# Reader
library(readr)

# Data processing
library(dplyr)

# Data visualisation
library(scales)
library(ggplot2)

library("stphtoolbox")
```

# Executive summary {.unnumbered}

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators. To achieve this, it would be necessary to have uniform grammar, pronunciation and more common words. If several languages coalesce, the grammar of the resulting language is more simple and regular than that of the individual languages. The new common language will be more simple and regular than the existing European languages. It will be as simple as Occidental; in fact, it will be Occidental. To an English person, it will seem like simplified English, as a sceptical Cambridge friend of mine told me what Occidental is. The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary.

The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators.

# Example Heading 1

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words.

## Example Heading 2

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators. To achieve this, it would be necessary to have uniform grammar, pronunciation and more common words. If several languages coalesce, the grammar of the resulting language is simpler and more regular than that of the individual languages.

### Example Heading 3

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation and their most common words. Everyone realises why a new common language would be desirable: one could refuse to pay expensive translators. To achieve this, it would be necessary to have uniform grammar, pronunciation and more common words. If several languages coalesce, the grammar of the resulting language is simpler and more regular than that of the individual languages.

#### Example Heading 4

The European languages are members of the same family. Their separate existence is a myth. For science, music, sport, etc., Europe uses the same vocabulary. The languages only differ in their grammar, their pronunciation.

# Graphical chart colors

```{r}
# Load Swiss TPH graphical chart colors
stph_colors <- stphtoolbox::stph_palette()
scales::show_col(stph_colors)
```

# Table design

```{r}
library(dplyr)
iris %>%
  head(10) %>% 
  knitr::kable()
```

```{r}
iris %>% 
ggplot2::ggplot() +
  ggplot2::geom_boxplot(mapping = ggplot2::aes(y = Sepal.Length,
                                               fill = stph_colors[[1]])) +
  ggplot2::theme_bw()
```

```{r}
iris %>% 
ggplot2::ggplot() +
  ggplot2::geom_bar(mapping = ggplot2::aes(x = Species,
                                           fill = Species)) +
  ggplot2::scale_fill_manual(values = unlist(stph_colors)) +
  ggplot2::theme_bw()
```
